---
title: "Final Report Main Analysis"
author: "Bin Yu"
---

## Load the data and cleaning

```{r}
rm(list = ls())
```

```{r}
library(frequency)
library(descr)
library(ggplot2)
```


```{r}
d <- read.csv("/Users/yubin/Desktop/Thesis/WTC_data.csv", stringsAsFactors = FALSE)
```

```{r}
library(tableone)
vars <- c("OAD", "severity2mid", "pacs_bin2m", "age911", "edu", "empl",
          "Race", "Sex", "dust_alt", "wtc.arrive.dust3", "wks11_cat")

factorVars <- c("edu", "empl", "Race", "Sex", "dust_alt", "wtc.arrive.dust3", "wks11_cat", 
                "OAD", "severity2mid", "pacs_bin2m")

table1 <- CreateTableOne(vars = vars, 
                         strata = "exp4_binary", 
                         data = d, 
                         factorVars = factorVars)

print(table1, showAllLevels = TRUE)

```

```{r}

library(naniar)

d$empl <- addNA(d$empl)
d$edu <- addNA(d$edu)

empl_dummies <- model.matrix(~ empl - 1, data = d)
edu_dummies <- model.matrix(~ edu - 1, data = d)
smoke_dummies <- model.matrix(~ smoke -1, data =d)

colnames(empl_dummies) <- paste0("empl_", levels(d$empl))
colnames(edu_dummies)  <- paste0("edu_", levels(d$edu))
colnames(smoke_dummies)  <- paste0("smoke_", levels(d$smoke))

d <- cbind(d, empl_dummies, edu_dummies, smoke_dummies)
# Convert depression and illness to factors if they are not already
d$depression <- as.factor(d$depression)
d$illness    <- as.factor(d$illness)

# Create dummy variables for depression and illness
depression_dummies <- model.matrix(~ depression - 1, data = d)
illness_dummies    <- model.matrix(~ illness - 1, data = d)

# Rename columns for clarity
colnames(depression_dummies) <- paste0("depression_", levels(d$depression))
colnames(illness_dummies)    <- paste0("illness_", levels(d$illness))

# Add the new dummy variables to the data frame
d <- cbind(d, depression_dummies, illness_dummies)
```


After cleaning the data, show the table 1 again:

```{r}
library(tableone)
d$BMI <- as.numeric(as.character(d$BMI))

vars <- c("OAD", "severity2mid", "pacs_bin2m", "age911", "edu", "empl",
          "race_binary", "ntrad","depression","illness", "Sex", "BMI","smoke")

factorVars <- c("edu", "empl", "race_binary", "Sex", "OAD", "severity2mid", "pacs_bin2m","ntrad","depression","illness","smoke")

d <- d[complete.cases(d[, c("exp4_binary", "OAD", "severity2mid", "pacs_bin2m", "age911", "edu", "empl", "Race", "Sex", "ntrad", "BMI")]), ]

table1 <- CreateTableOne(vars = vars, 
                         strata = "exp4_binary", 
                         data = d, 
                         factorVars = factorVars)

print(table1, showAllLevels = TRUE)
```

---

## Chain Mediation Analysis using the paths Package

In this analysis, we assume the following causal chain:
  
\[
\text{exp4\_binary} \longrightarrow \text{OAD} \longrightarrow \text{severity2mid} \longrightarrow \text{pacs\_bin2m}
\]

where  
- **exp4_binary** is the exposure,  
- **OAD** is the first mediator,  
- **severity2mid** is the second mediator, and  
- **pacs_bin2m** is the outcome.  

Covariates include **age911**, **edu_1**, **edu_2**, **edu_3**, **edu_99**, **empl_1**, and **empl_99**.

We will use GLMs to estimate the following models:

1. **Mediator 1 Model (OAD):**
\[
\text{logit}\,\Pr\{\text{OAD}=1 \mid \text{exp4\_binary}, C\} = \alpha_0 + \alpha_1\,\text{exp4\_binary} + \gamma_1^\top C,
\]
where \( C \) denotes the covariates.

2. **Mediator 2 Model (severity2mid):**
\[
\text{logit}\,\Pr\{\text{severity2mid}=1 \mid \text{exp4\_binary}, \text{OAD}, C\} = \beta_0 + \beta_1\,\text{exp4\_binary} + \beta_2\,\text{OAD} + \gamma_2^\top C.
\]

3. **Outcome Model (pacs\_bin2m):**
\[
\text{logit}\,\Pr\{Y=1 \mid \text{exp4\_binary}, \text{OAD}, \text{severity2mid}, C\} = \delta_0 + \delta_1\,\text{exp4\_binary} + \delta_2\,\text{OAD} + \delta_3\,\text{severity2mid} + \gamma_3^\top C.
\]

Additionally, we fit a propensity score model for the exposure:
\[
\text{logit}\,\Pr\{\text{exp4\_binary}=1 \mid C\} = \eta_0 + \eta^\top C.
\]

The following R code implements these steps using the **paths** package.

# Exposure - OAD - Severity with DxM interaction
```{r}

set.seed(60615)
library(paths)

d$age911_std <- as.numeric(scale(d$age911))
d$BMI_std <- as.numeric(scale(d$BMI))
# Define the mediators as a list of variable names (chain mediation with two mediators)
mediators <- list("OAD")
# Define formulas for each GLM
formula_m0 <- severity2mid ~ exp4_binary + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std
# Mediator 1 model: OAD
formula_m1 <- severity2mid ~ (exp4_binary * OAD) + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std

# Propensity score model for the exposure
formula_ps <- exp4_binary ~ age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std

# Fit the GLMs
glm_m0 <- glm(formula_m0, family = binomial("logit"), data = d)
glm_m1 <- glm(formula_m1, family = binomial("logit"), data = d)

glm_ymodels <- list(glm_m0, glm_m1)

# Fit the propensity score model
glm_ps <- glm(formula_ps, family = binomial("logit"), data = d)
paths_glm <- paths(a = "exp4_binary", y = "severity2mid", m = mediators,
                   glm_ymodels, ps_model = glm_ps, data = d, nboot = 1000)

summary(paths_glm)
plot(paths_glm)
```
```{r}
sens_paths <- sens(paths_glm, confounded = "M1", estimand = "via M1", gamma_values = - seq(-0.5, 0.5, 0.002), eta_values = seq(-0.5, 0.5, 0.002))

plot(sens_paths)
```

# Exposure - OAD - Severity without DxM interaction
```{r}
set.seed(60615)

# Define the mediators as a list of variable names (chain mediation with two mediators)
mediators <- list("OAD")
# Define formulas for each GLM
formula_m0 <- severity2mid ~ exp4_binary + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std
# Mediator 1 model: OAD
formula_m1 <- severity2mid ~ exp4_binary + OAD + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std

# Propensity score model for the exposure
formula_ps <- exp4_binary ~ age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std

# Fit the GLMs
glm_m0 <- glm(formula_m0, family = binomial("logit"), data = d)
glm_m1 <- glm(formula_m1, family = binomial("logit"), data = d)

glm_ymodels <- list(glm_m0, glm_m1)

# Fit the propensity score model
glm_ps <- glm(formula_ps, family = binomial("logit"), data = d)
paths_glm <- paths(a = "exp4_binary", y = "severity2mid", m = mediators,
                   glm_ymodels, ps_model = glm_ps, data = d, nboot = 1000)

summary(paths_glm)
plot(paths_glm)
```
```{r}
sens_paths <- sens(paths_glm, confounded = "M1", estimand = "via M1", gamma_values = - seq(-0.5, 0.5, 0.002), eta_values = seq(-0.5, 0.5, 0.002))

plot(sens_paths)
```


# Exposure - OAD - Severity - Long COVID with DxM interaction
```{r, message=FALSE, warning=FALSE}

set.seed(60615)


# Define the mediators as a list of variable names (chain mediation with two mediators)
mediators <- list("OAD", "severity2mid")
# Define formulas for each GLM
formula_m0 <- pacs_bin2m ~ exp4_binary + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std
# Mediator 1 model: OAD
formula_m1 <- pacs_bin2m ~ (exp4_binary * OAD) + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std

# Mediator 2 model: severity2mid
formula_m2 <- pacs_bin2m ~ exp4_binary * (OAD + severity2mid) + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std 
# Propensity score model for the exposure
formula_ps <- exp4_binary ~ age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std

# Fit the GLMs
glm_m0 <- glm(formula_m0, family = binomial("logit"), data = d)
glm_m1 <- glm(formula_m1, family = binomial("logit"), data = d)
glm_m2 <- glm(formula_m2, family = binomial("logit"), data = d)

glm_ymodels <- list(glm_m0, glm_m1, glm_m2)

# Fit the propensity score model
glm_ps <- glm(formula_ps, family = binomial("logit"), data = d)

# Run the causal paths analysis using the paths package.
# The exposure is 'exp4_binary' and the outcome is 'pacs_bin2m'.
# We use 1000 bootstrap replicates for inference.
paths_glm <- paths(a = "exp4_binary", y = "pacs_bin2m", m = mediators,
                   glm_ymodels, ps_model = glm_ps, data = d, nboot = 1000)

summary(paths_glm)

plot(paths_glm)
```
```{r}
sens_paths <- sens(paths_glm, confounded = "M1", estimand = "via M1", gamma_values = - seq(-0.5, 0.5, 0.002), eta_values = seq(-0.5, 0.5, 0.002))

plot(sens_paths)
```

# Exposure - OAD - Severity - Long COVID without DxM interaction
```{r, message=FALSE, warning=FALSE}

set.seed(60615)
library(paths)
d$age911_std <- as.numeric(scale(d$age911))
d$BMI_std <- as.numeric(scale(d$BMI))

# Define the mediators as a list of variable names (chain mediation with two mediators)
mediators <- list("OAD", "severity2mid")
# Define formulas for each GLM
formula_m0 <- pacs_bin2m ~ exp4_binary + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std
# Mediator 1 model: OAD
formula_m1 <- pacs_bin2m ~ exp4_binary + OAD + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std

# Mediator 2 model: severity2mid
formula_m2 <- pacs_bin2m ~ exp4_binary + OAD + severity2mid + age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std 
# Propensity score model for the exposure
formula_ps <- exp4_binary ~ age911_std + edu_1 + edu_2 + edu_3 + edu_99 + empl_1 + empl_99 + race_binary + ntrad + depression_1 + depression_99 + illness_1 + illness_99 + BMI_std

# Fit the GLMs
glm_m0 <- glm(formula_m0, family = binomial("logit"), data = d)
glm_m1 <- glm(formula_m1, family = binomial("logit"), data = d)
glm_m2 <- glm(formula_m2, family = binomial("logit"), data = d)

glm_ymodels <- list(glm_m0, glm_m1, glm_m2)

# Fit the propensity score model
glm_ps <- glm(formula_ps, family = binomial("logit"), data = d)

# Run the causal paths analysis using the paths package.
# The exposure is 'exp4_binary' and the outcome is 'pacs_bin2m'.
# We use 1000 bootstrap replicates for inference.
paths_glm <- paths(a = "exp4_binary", y = "pacs_bin2m", m = mediators,
                   glm_ymodels, ps_model = glm_ps, data = d, nboot = 1000)

summary(paths_glm)

plot(paths_glm)
```
```{r}
sens_paths <- sens(paths_glm, confounded = "M1", estimand = "via M1", gamma_values = - seq(-0.5, 0.5, 0.002), eta_values = seq(-0.5, 0.5, 0.002))

plot(sens_paths)
```


